\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
% \usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tgpagella}

% Choose a font

% \usepackage[familydefault,regular]{Chivo}
% \usepackage[T1]{fontenc}

% \usepackage[T1]{fontenc}
% \usepackage{accanthis}

\usepackage[T1]{fontenc}
\usepackage[light]{antpolt}

% \usepackage{fontspec}
% \setmainfont{QTEurotype}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% TAB FORMATTING
\setlength{\parindent}{0.2em}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1:}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoTitle}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeDoubleSubheading}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
      \textit{\small#5} & \textit{\small#6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemNoBullet}[1]{%
    \hspace*{\dimexpr-\labelsep -\labelwidth}%
    \item[]\small{#1 \vspace{-2pt}}%
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]\setlength\itemsep{1mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}
    {
    l@{\extracolsep{\fill}}l
    @{\extracolsep{6pt}}r
    l@{\extracolsep{\fill}}l
    @{\extracolsep{6pt}}r
    @{\extracolsep{6pt}}r
    @{\extracolsep{6pt}}r
    }

\textbf{\LARGE Felipe Scrochio Custódio}
& Email: & \href{mailto:felipe.crochi@gmail.com}{felipe.crochi@gmail.com} \\
{\large Software Engineer}
& Github: & \href{https://github.com/felipecustodio}{github.com/felipecustodio} \\
& LinkedIn: & \href{https://www.linkedin.com/in/fscustodio}{linkedin.com/in/fscustodio} \\

\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubHeadingListStart
  \resumeSubheading
      {Zyte \href{https://zyte.com}{(zyte.com)}}{Remote, Ireland}
      {Full time - Mid. Software Engineer}{Jul. 2022 - Present}
      \resumeItemListStart
        \resumeItemNoTitle
            {
            Developed and maintained hundreds of Scrapy spiders across multiple Python codebases, optimizing data extraction processes.
            }
        \resumeItemNoTitle
            {
            Built projects from scratch, addressed bugs, and performed code refactoring, significantly enhancing code quality and project scalability.
            }
        \resumeItemNoTitle
            {
            Communicated directly with clients to understand project specifications, delivering tailored solutions that met dynamic and evolving requirements.
            }
        \resumeItemNoTitle
            {
            Collaborated with a remote, multicultural team spanning multiple time zones, utilizing tools like Slack, Jira, and Meet to ensure consistent communication and seamless project delivery.
            }
      \resumeItemListEnd
  \resumeSubheading
      {Birdie \href{https://birdie.ai}{(birdie.ai)}}{Remote, Brazil}
      % {Full time - Jr. Software Engineer}{Jan. 2022 - Jul. 2022}
      % {Internship}{Jul. 2021 - Jan. 2022}
      {Full time - Jr. Software Engineer}{Jul. 2021 - Jul. 2022}
      \resumeItemListStart
        \resumeItemNoTitle
          {
          Utilized Scrapy and Python to develop and manage data scraping spiders across diverse sources such as app stores, e-commerce sites, forums, and blogs.
          }
        \resumeItemNoTitle
          {
           Contributed to the design and implementation of an in-house distributed crawling architecture, resulting in a significant performance boost, enabling the scraping of millions of pages per week. Implemented real-time monitoring dashboards for enhanced visibility.
          }
        \resumeItemNoTitle
          {
          Worked in a fast-paced B2B startup environment, communicating directly with stakeholders to discuss project requirements and deliver data on time.
          }
      \resumeItemListEnd
    \resumeSubheading
      {Raccoon Marketing Digital \href{https://birdie.ai}{(raccoon.ag)}}{São Carlos, São Paulo, Brazil}
      {Internship - Business Intelligence team}{Apr 2019 - Aug 2020}
      \resumeItemListStart
        \resumeItemNoTitle
        {
        Developed data extractor for various sources, including APIs, databases, and web pages, to build datasets for both business clients and internal stakeholders in Analytics pipelines.
        }
        \resumeItemNoTitle
          {
          Designed dashboards, automated spreadsheets, and reports, merging data from different sources such as Google Sheets, and querying data from Google BigQuery to provide real-time marketing insights to client companies.
          }
          \resumeItemNoTitle
          {
          Developed data governance tools using data lineage and network visualizations for all data pipelines to reduce maintenance efforts, highlight bottlenecks, and lower storage costs.
          }
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ICMC USP - University of São Paulo}{São Carlos, São Paulo, Brazil}
      {Master of Business Administration (MBA) }{Jul. 2024 -- Oct. 2025}

      \resumeItemListStart
        \resumeSubItemNoBullet
          {MBA in topics of Advanced AI and Big Data, focused on current methodologies in AI, data storage, and processing with practical implementation exercises.}
      \resumeItemListEnd

    \resumeSubheading
      {ICMC USP - University of São Paulo}{São Carlos, São Paulo, Brazil}
      {Bachelor of Science in Computer Science (BSc)}{Mar. 2015 -- Dec. 2021}

      \resumeItemListStart
        \resumeSubItemNoBullet
          {Received a Bachelor's Degree from the Instituto de Ciências Matemáticas e de Computação, at the University of São Paulo (ICMC - USP), one of the most important Brazilian institutions in the fields of STEM.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
 
%-----------PROJECTS-----------------
% \section{Extracurricular Activities}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%     {PvP - Piratas do Vale do Pinhal}{São Carlos, SP, Brazil}
%       {https://github.com/pirataspinhal}{Fev 2016 - Present}
    
%     \resumeItemListStart
%       \resumeItemNoTitle
%         {
%         An interdisciplinary studies group on computer science, focusing on doing in-depth exploration of topics beyond those already covered by the university courses, aiming for a more complete and cooperative learning experience.
%         }
%     \resumeItemListEnd
%   \resumeSubHeadingListEnd

%-------- SKILLS------------
\section{Skills \& Competencies}
 \resumeItemListStart
    \resumeItem{Languages}{}\vspace{-3pt}{
        \resumeItemListStart
            \resumeItem{Portuguese}{Native}
            \resumeItem{English}{Full Professional Proficiency}
        \resumeItemListEnd
    }
    \resumeItem{Skills and Tools}{}\vspace{-3pt}{
        \resumeItemListStart
            \resumeItemNoTitle
            {Python | SQL | Git | Linux | Google Cloud Platform (BigQuery, Cloud Functions, Storage, App Engine) | AWS (Firehose, Athena, S3) | Microsoft Azure (AKS, VMs, Functions) | Web scraping (Scrapy, Puppeteer, Selenium) | DevOps, Infrastructure (Docker, Kubernetes, Terraform) | CI/CD (ArgoCD, Gitlab) | Messaging and Caching (Redis) | Web Frameworks (FastAPI, Flask) | Monitoring (Grafana, InfluxDB, Loki) | Testing (Pytest, Unit Tests)}
        \resumeItemListEnd
    }
 \resumeItemListEnd

%-------------------------------------------
\end{document}